\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
Results table lolololololol2 :D

\section{Table with computation times}
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
products72 & 5.0530 sec & 5.4318 sec & 0.0207 sec\\
torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
\end{tabular}
\end{appendices}

>>>>

\section{Table with computation times}
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
products72 & 7.5950 sec & 7.5198 sec & 0.0275 sec\\
torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
\end{tabular}
\end{appendices}
